---
title: "Justin Gregoire's CV"
date: "`r Sys.Date()`"
format:
  html:
    link-external-icon: true
    link-external-newwindow: true
    link-external-filter: '^(?:http:|https:)\/\/www\.quarto\.org\/custom'
params: 
  your_name: 
    value: "Justin Gregoire"
  pdf_export: 
    value: TRUE
  sheet_ss_id: 
    value: "1SqkIDpyVfurLA0DXRgcsZ9aba_Bk9bvak0sGRCLsVX0"
  online_link:
    value: "https://justingregoire.me/resume.html"
  pdf_location: 
    value: "https://github.com/jtgregoire93/justingregoire.me/raw/main/pdf/jgregoire_resume.pdf"
output:
  pagedown::html_resume:
    css: ['~/Documents/GitHub/justingregoire.me/resume_gen/css/custom_resume.css','~/Documents/GitHub/justingregoire.me/resume_gen/css/styles.css','resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(googlesheets4)
library(crayon)
library(googledrive)
library(gluedown)
library(fontawesome)
library(tippy)


# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- params$pdf_export
your_name <- params$your_name
# ss id of your google sheet, using mine here

# Holds all the links that were inserted for placement at the end

source('~/Documents/GitHub/justingregoire.me/resume_gen/parsing_functions.R') # Functions for building sections from CSV data

gs4_auth(email = "jtgregoire93@gmail.com")

# Refactored code
position_data <- read_sheet(params$sheet_ss_id, sheet = "entries", skip = 1) %>% 
  filter(in_resume) %>% 
  mutate(
    section = case_when(
      section %in% c('industry_positions') ~ 'positions', 
      TRUE ~ section
    )
  ) 

intro_text <- read_sheet(params$sheet_ss_id, sheet = "text_blocks", skip = 1) %>%
  select("text") %>% 
  as.character()

skills <- read_sheet(params$sheet_ss_id, sheet = "skills", skip = 1) 

contact_info <-
  read_sheet(params$sheet_ss_id, sheet = "contact_info", skip = 1)
location <-
  contact_info %>% filter(loc == 'location')  %>% select(entry, link) 
email <-
  contact_info %>% filter(loc == 'email')  %>% select(entry, link)  
phone <-
  contact_info %>% filter(loc == 'phone')  %>% select(entry, link)  
linkedin <-
  contact_info %>% filter(loc == 'linkedin')  %>% select(entry, link)  
github <-
  contact_info %>% filter(loc == 'github')  %>% select(entry, link)  
calendly <-
  contact_info %>% filter(loc == 'calendly')  %>% select(entry, link) 

location <- contact_info %>% 
            filter(loc == 'location')  %>% 
            select(entry, link) 

email <- contact_info %>% 
         filter(loc == 'email')

```

# Aside

### Contact {#contact}

|                                                                                                                 |                                                                                    |
|-----------------------------------------------------------------------------------------------------------------|------------------------------------------------------------------------------------|
| [![Mail](svg/envelope.svg){alt="Mail" width="50%"}](mailto:jtgregoire93@gmail.com)                              | `r email %>% select(entry) %>% as.character()`                                     |
| ![Phone](svg/phone.svg){alt="Phone" width="50%"}                                                                | `r phone %>% select(entry)`                                                        |
| [![Site](svg/compass-regular.svg){alt="Site" width="50%"}](https://justingregoire.me/)                          | [justingregoire.me](https://justingregoire.me/){style="color: #444"}               |
| [![Calendar](svg/calendar-days.svg){alt="Calendar" width="50%"}](https://calendar.app.google/J4eY2975fDGTM3SM9) | [Availability](https://calendar.app.google/J4eY2975fDGTM3SM9){style="color: #444"} |
| [![Github](svg/github.svg){alt="Github" width="50%"}](https://github.com/jtgregoire93)                          | [Github](https://github.com/jtgregoire93){style="color: #444"}                     |
| [![Linkedin](svg/linkedin-in.svg){alt="Linkedin" width="50%"}](https://www.linkedin.com/in/justin-gregoire/)    | [Linkedin](https://www.linkedin.com/in/justin-gregoire/){style="color: #444"}      |

### Education {data-icon="graduation-cap" data-concise="true"}

-   **`r knitr::asis_output(position_data %>% filter(section == 'education') %>% pull("institution") %>% paste(collapse=", "))`**

-   `r knitr::asis_output(position_data %>% filter(section == 'education') %>% pull("title") %>% paste(collapse=", "))`

-   `r knitr::asis_output(paste0(position_data %>% filter(section == 'education') %>% pull("start"), '-', position_data %>% filter(section == 'education') %>% pull("end")) %>% paste(collapse=", "))`

### Technical Skills

-   `r knitr::asis_output(skills %>% filter(loc == 'technical') %>% pull("skill1") %>% paste(collapse=", "))`

-   `r knitr::asis_output(skills %>% filter(loc == 'technical') %>% pull("skill2") %>% paste(collapse=", "))`

-   `r knitr::asis_output(skills %>% filter(loc == 'technical') %>% pull("skill3") %>% paste(collapse=", "))`

### Strategic Skills

-   `r knitr::asis_output(skills %>% filter(loc == 'strategic') %>% pull("skill1") %>% paste(collapse=", "))`

-   `r knitr::asis_output(skills %>% filter(loc == 'strategic') %>% pull("skill2") %>% paste(collapse=", "))`

-   `r knitr::asis_output(skills %>% filter(loc == 'strategic') %>% pull("skill3") %>% paste(collapse=", "))`

### Toolset

-   `r knitr::asis_output(skills %>% filter(loc == 'toolset') %>% pull("skill1") %>% paste(collapse=", "))`

-   `r knitr::asis_output(skills %>% filter(loc == 'toolset') %>% pull("skill2") %>% paste(collapse=", "))`

# Main

## `r your_name` {#title}

```{r message=FALSE, warning=FALSE}
cat(paste0(intro_text, sep = "\n"))
```

## Professional Experience {data-icon="suitcase"}

```{r comment=NA, results='asis'}
position_data %>% print_section('positions') 
```
